STJ2012 analysis

### 2016-08-01 analysis/STJ2012_analysis.Rmd
continue integrating 100% OTU data analysis

#### Filter OTUs by minimum count
```{r filter_taxa}
# Set threshold count
n <- 3
# Identify OTUs below threshold count
taxa97 <- taxa_sums(phy97.f)[which(taxa_sums(phy97.f) >= n)]  
taxa100 <- taxa_sums(phy100.f)[which(taxa_sums(phy100.f) >= n)]
# Remove taxa below threshold count
phy97.f <- prune_taxa(names(taxa97), phy97.f)  
phy100.f <- prune_taxa(names(taxa100), phy100.f)  
```

@@

# Data analysis
## Community composition barplots
Here the composition of each sample is plotted as a horizontal bar, sorted by species and shore. Each segment of the bar represents an individual OTU. In the lefthand plot, all OTUs are colored by clade, in the right OTU, all OTUs are given a unique color.
```{r cladecomp, fig.height=6, fig.width=8}
# Define function to plot Symbiodinium community composition
composition <- function(phy, col, legend=T) {
  samdat <- data.frame(sample_data(phy))
  samdat$Genus <- factor(samdat$Genus, levels=rev(levels(samdat$Genus)))
  samdat$Species <- factor(samdat$Species, levels=rev(levels(samdat$Species)))
  samdat$Shore <- factor(samdat$Shore, levels=rev(levels(samdat$Shore)))
  samdat <- samdat[with(samdat, order(Genus, Species, Shore)), ]
  typerelabund <- as.matrix(otu_table(phy)[order(data.frame(tax_table(phy))$Subtype), 
                                           rownames(samdat)])
  shorebreaks <- c(as.character(samdat$Shore), "X")==c("X", as.character(samdat$Shore))
  shorebreaks <- which(shorebreaks==F) - 1
  spbreaks <- c(which(duplicated(samdat$Species)==F) - 1, nrow(samdat))
  # Make Barplot
  barplot(typerelabund, horiz=T, space=0, axes=F,axisnames=F, yaxs="i", col=col)
  rect(0, 0, par("usr")[2], par("usr")[4], lwd=1, xpd=T)
  axis(side=1, at=seq(0, 1, 0.1), line=0, tck=-0.025, mgp=c(0,0.25,0), cex.axis=0.7)
  mtext(side=1, "Relative abundance", cex=0.7, line=1)
  # Add legend
  if (legend==T) {
    legend(x=par("usr")[2]/2, y=par("usr")[4], xjust=0.5, yjust=0.25, horiz=T, bty="n", xpd=T, 
           cex=0.7, legend=c("A", "B", "C", "D", "F"), fill=taxcolors, x.intersp=0.5)
    legend(x=par("usr")[2]-0.03, y=par("usr")[4], xjust=0, yjust=0.1, bty="n", xpd=T, cex=0.6, 
           pt.cex=0.6, legend=c("N Shore", "S Shore"), fill=c(0, "gray40"), y.intersp=0.7, 
           x.intersp=0.3)
  }
  # Add grouping bars for Shore
  for (i in 1:length(shorebreaks)) {
    lines(c(0, 1), c(shorebreaks[i], shorebreaks[i]), lty=2, lwd=0.25)
    rect(1.01, shorebreaks[i], 1.04, shorebreaks[i+1], col=rep(c("gray40", 0), 50)[i], 
         lwd=0.25, xpd=T)
  }
  # Add lines to separate species and species names
  for (i in 1:length(spbreaks)) {
    lines(c(0, 1.07), c(spbreaks[i], spbreaks[i]), xpd=T, type="l", lwd=0.4)
    text(1.03, (spbreaks[i] + spbreaks[i+1]) / 2, xpd=T, pos=4, cex=0.6,
        labels=paste(samdat$Genus[which(duplicated(samdat$Species)==F)][i], "\n",
                    samdat$Species[which(duplicated(samdat$Species)==F)][i], sep=""))
  }
}

par(mfrow=c(1,2), mar=c(2, 1.5, 2, 5), lwd=0.1, cex=0.7)
composition(phy97.f.p, col=taxcolors[data.frame(tax_table(phy97.f.p))[order(data.frame(tax_table(phy97.f.p))$Subtype), ]$Clade], legend=T)
composition(phy97.f.p, col=rainbow(ntaxa(phy97.f.p)), legend=F)

@@

```{r, cache=T}
par(mfrow=c(1,2), mar=c(2, 1.5, 2, 5), lwd=0.1, cex=0.7)
composition(phy100.f.p, col=taxcolors[data.frame(tax_table(phy100.f.p))[order(data.frame(tax_table(phy100.f.p))$Subtype), ]$Clade], legend=T)
composition(phy100.f.p, col=rainbow(ntaxa(phy100.f.p)), legend=F)
phy.f.p <- phy97.f.p
phy.f.t <- phy97.f.t
```

## Differences between species and shores
Whether *Symbiodinium* communities differ among species, or differ between north vs. south shores within species, is evaluated here using permutational analysis of variance (PERMANOVA).

```{r permanovas, cache=T}
# PERMANOVA for differences among species? Post-hoc: which spp are different?

permanova.spp.t <- adonis(phyloseq::distance(phy.f.t, "bray") ~ Species, 
                          data=as(sample_data(phy.f.t), "data.frame"), permutations=9999)

dmat <- as(phyloseq::distance(phy.f.t, "bray"), "matrix")
df <- as(sample_data(phy.f.t), "data.frame")

pairs <- data.frame(t(combn(levels(df$Species), 2)), stringsAsFactors=F)
p.pairs <- setNames(rep(NA, nrow(pairs)), with(pairs, paste(X1, X2, sep='-')))

for (i in 1:nrow(pairs)) {
  dfs <- subset(df, Species %in% c(pairs[i,1], pairs[i,2]))
  dmats <- dmat[rownames(dfs), rownames(dfs)]
  set.seed(152470)
  permanova <- adonis(dmats ~ Species, data=dfs, permutations=999)
  p.pairs[i] <- permanova$aov.tab$`Pr(>F)`[1]
}

multcompLetters(p.pairs)

# Compute within- and between-pool statistics for each Species
shorestats <- data.frame(matrix(dimnames=list(levels(data.frame(sample_data(phy.f.t))$Species), 
                                              c("Species", "n", "overall", "within", 
                                                "between", "R2", "bd", "p")), ncol=8, nrow=10))
for (i in 1:nlevels(data.frame(sample_data(phy.f.t))$Species)) {
  sp <- levels(data.frame(sample_data(phy.f.t))$Species)[i]
  shorestats$Species[i] <- sp
  phy.f.t.species <- subset_samples(phy.f.t, Species==sp)  # Set temp phyloseq object
  shorestats$n[i] <- nsamples(phy.f.t.species)
  md <- meandist(phyloseq::distance(phy.f.t.species, "bray"), 
                 sample_data(phy.f.t.species)$Shore)
  shorestats$within[i] <- summary(md)$W  # Weighted mean dissimilarity within both Pools
  shorestats$between[i] <- summary(md)$B  # Mean dissimilarity between Pools
  shorestats$overall[i] <- summary(md)$D  # Overall dissimilarity
  if (nlevels(as(sample_data(phy.f.t.species), "data.frame")$Shore) > 1) {
    set.seed(70235)
    permanova <- adonis(phyloseq::distance(phy.f.t.species, "bray") ~ Shore, 
                        data=as(sample_data(phy.f.t.species), "data.frame"), permutations=999)
    shorestats$R2[i] <- permanova$aov.tab$"R2"[1]  # PERMANOVA partial R-squared
    shorestats$p[i] <- permanova$aov.tab$"Pr(>F)"[1]  # PERMANOVA p-value
    bd <- betadisper(phyloseq::distance(phy.f.t.species, "bray"),
                     group=as(sample_data(phy.f.t.species), "data.frame")$Shore)
    shorestats$bd[i] <- TukeyHSD(bd)$group[4]
  } else {
    shorestats$R2[i] <- NA
    shorestats$p[i] <- NA
    shorestats$bd[i] <- NA
  }
}
knitr::kable(shorestats)  # dendrogyra, porites furcata, and siderastrea siderea differ by shore
```

## Beta diversity
Beta diversity is evaluated here as the multivariate dispersion of samples within a coral species group. Principal coordinate analysis on Bray-Curtis dissimilarities is used to calculate average distance-to-centroid values for each species group, which are then compared statistically by a permutation test. This analysis is implemented using betadisper() in the vegan package, based on [Anderson (2006)](dx.doi.org/10.1111/j.1541-0420.2005.00440.x).
```{r betadisper, cache=T, fig.width=4, fig.height=4}
# Calculate distances to species centroids for each sample in principal coordinate space
sambd <- betadisper(d=vegdist(t(otu_table(phy.f.t)), method="bray"), 
                    group=data.frame(sample_data(phy.f.t))$Species, type="centroid",
                    bias.adjust=TRUE)
# Calculate each species' mean distance to centroid and standard error
sambdsumm <- aggregate(data.frame(mean=sambd$distances), by=list(group=sambd$group), FUN=mean)
sambdsumm$se <- aggregate(sambd$distances, by=list(group=sambd$group), 
                      FUN=function(x) sd(x)/sqrt(length(x)))$x
# Determine order of decreasing mean dispersion
sambdsumm.ord <- sambdsumm[order(sambdsumm$mean, decreasing=T), ]
# Update betadisper object with species in decreasing order of mean dispersion
sambd <- betadisper(d=vegdist(t(otu_table(phy.f.t)), method="bray"), 
                    group=factor(data.frame(sample_data(phy.f.t))$Species, levels=as.character(sambdsumm.ord$group)), type="centroid", bias.adjust=TRUE)
# Use permutations to perform pairwise comparisons of group mean dispersions
sampt <- permutest(sambd, pairwise=T)
saml <- multcompLetters(sampt$pairwise$permuted)

@@

```{r strigosa}
dstr97 <- subset_samples(phy97.f.p, Species=="strigosa")
plot_bar(dstr97, x="Sample", y="Abundance", fill="OTU")
plot_bar(dstr97, x="Sample", y="Abundance", fill="Subtype")
# D strigosa hosted B1, B24, B35, B38, and C3 in Finney et al.... B25, B35, and B38 are missing from ref database.
# Also try 100% OTUs -- must filter more first...
#dstr100.f <- subset_samples(phy100.f, Species=="strigosa")
#dstr100.f.p <- transform_sample_counts(dstr100.f, function(x) x/sum(x))
#dstr100.f.p.f <- prune_taxa(rownames(otu_table(dstr100.f.p))[which(rowSums(otu_table(dstr100.f.p)) > 0.01)],
#                            dstr100.f.p)
#  
#plot_bar(dstr100.f.p.f, x="Sample", y="Abundance", fill="OTU")
#plot_bar(dstr100, x="Sample", y="Abundance", fill="Subtype")
#sample_names(dstr100.f)
#subset_samples(dstr100, Sample=="7")
#otu_table(dstr100.f)
#dstr100.f.p <- transform_sample_counts(dstr100.f, function(x) x/sum(x))
#colSums(otu_table(dstr100.f.p)[rowSums(otu_table(dstr100.f.p)) > 0.1, ])

@@

## Niche breadth of *Symbiodinium*
```{r nichebreadth}
# Mean dispersion of clades
otubd <- betadisper(d=vegdist(otu_table(phy.f.t), method="bray"), 
                    group=data.frame(tax_table(phy.f.t))$Clade, type="centroid")
otubd

# Number of samples each OTU appears in
nsamp <- data.frame(n=rowSums(otu_table(phy.f.t) != 0))
nsamp$Subtype <- data.frame(tax_table(phy.f.t))[rownames(nsamp), "Subtype"]
nsamp[order(nsamp$n, decreasing=T), ]
nsamp
?order

@@

plot_richness(phy.f, x="Species")

>>>>

#### Filter OTUs by minimum count
```{r filter_taxa}
# Set threshold count
n <- 10
# Identify OTUs below threshold count
taxa97 <- taxa_sums(phy97.f)[which(taxa_sums(phy97.f) >= n)]  
taxa100 <- taxa_sums(phy100.f)[which(taxa_sums(phy100.f) >= n)]
# Remove taxa below threshold count
phy97.f <- prune_taxa(names(taxa97), phy97.f)  
phy100.f <- prune_taxa(names(taxa100), phy100.f)  
```

@@

# Data analysis
## Community composition barplots
Here the composition of each sample is plotted as a horizontal bar, sorted by species and shore. Each segment of the bar represents an individual OTU. In the lefthand plot, all OTUs are colored by clade, in the right OTU, all OTUs are given a unique color.
```{r cladecomp97, cache=T, fig.height=6, fig.width=8}
# Define function to plot Symbiodinium community composition
composition <- function(phy, col, legend=T) {
  samdat <- data.frame(sample_data(phy))
  samdat$Genus <- factor(samdat$Genus, levels=rev(levels(samdat$Genus)))
  samdat$Species <- factor(samdat$Species, levels=rev(levels(samdat$Species)))
  samdat$Shore <- factor(samdat$Shore, levels=rev(levels(samdat$Shore)))
  samdat <- samdat[with(samdat, order(Genus, Species, Shore)), ]
  typerelabund <- as.matrix(otu_table(phy)[order(data.frame(tax_table(phy))$Subtype), 
                                           rownames(samdat)])
  shorebreaks <- c(as.character(samdat$Shore), "X")==c("X", as.character(samdat$Shore))
  shorebreaks <- which(shorebreaks==F) - 1
  spbreaks <- c(which(duplicated(samdat$Species)==F) - 1, nrow(samdat))
  # Make Barplot
  barplot(typerelabund, horiz=T, space=0, axes=F,axisnames=F, yaxs="i", col=col)
  rect(0, 0, par("usr")[2], par("usr")[4], lwd=1, xpd=T)
  axis(side=1, at=seq(0, 1, 0.1), line=0, tck=-0.025, mgp=c(0,0.25,0), cex.axis=0.7)
  mtext(side=1, "Relative abundance", cex=0.7, line=1)
  # Add legend
  if (legend==T) {
    legend(x=par("usr")[2]/2, y=par("usr")[4], xjust=0.5, yjust=0.25, horiz=T, bty="n", xpd=T, 
           cex=0.7, legend=c("A", "B", "C", "D", "F"), fill=taxcolors, x.intersp=0.5)
    legend(x=par("usr")[2]-0.03, y=par("usr")[4], xjust=0, yjust=0.1, bty="n", xpd=T, cex=0.6, 
           pt.cex=0.6, legend=c("N Shore", "S Shore"), fill=c(0, "gray40"), y.intersp=0.7, 
           x.intersp=0.3)
  }
  # Add grouping bars for Shore
  for (i in 1:length(shorebreaks)) {
    lines(c(0, 1), c(shorebreaks[i], shorebreaks[i]), lty=2, lwd=0.25)
    rect(1.01, shorebreaks[i], 1.04, shorebreaks[i+1], col=rep(c("gray40", 0), 50)[i], 
         lwd=0.25, xpd=T)
  }
  # Add lines to separate species and species names
  for (i in 1:length(spbreaks)) {
    lines(c(0, 1.07), c(spbreaks[i], spbreaks[i]), xpd=T, type="l", lwd=0.4)
    text(1.03, (spbreaks[i] + spbreaks[i+1]) / 2, xpd=T, pos=4, cex=0.6,
        labels=paste(samdat$Genus[which(duplicated(samdat$Species)==F)][i], "\n",
                    samdat$Species[which(duplicated(samdat$Species)==F)][i], sep=""))
  }
}

par(mfrow=c(1,2), mar=c(2, 1.5, 2, 5), lwd=0.1, cex=0.7)

# Plot composition of 97% OTUs colored by clade
composition(phy97.f.p, col=taxcolors[data.frame(tax_table(phy97.f.p))[order(data.frame(tax_table(phy97.f.p))$Subtype), ]$Clade], legend=T)

# Plot composition of 97% OTUs colored by OTU
composition(phy97.f.p, col=rainbow(ntaxa(phy97.f.p)), legend=F)

@@

```{r cladecomp100, cache=T, fig.height=6, fig.width=8}
par(mfrow=c(1,2), mar=c(2, 1.5, 2, 5), lwd=0.1, cex=0.7)
# Plot composition of 100% OTUs colored by clade
composition(phy100.f.p, col=taxcolors[data.frame(tax_table(phy100.f.p))[order(data.frame(tax_table(phy100.f.p))$Subtype), ]$Clade], legend=T)

# Plot composition of 100% OTUs colored by OTU
composition(phy100.f.p, col=rainbow(ntaxa(phy100.f.p)), legend=F)
```

## Differences between species
Whether *Symbiodinium* communities differ among species is evaluated using permutational analysis of variance (PERMANOVA).

```{r permanovas, cache=T}
# PERMANOVA for difference among species
sppdiffs <- function(phy) {
  permanova.spp.t <- adonis(phyloseq::distance(phy, "bray") ~ Species, 
                          data=as(sample_data(phy), "data.frame"), permutations=9999)
  permanova.spp.t
  # Pairwise PERMANOVA tests for differences between species
  dmat <- as(phyloseq::distance(phy, "bray"), "matrix")
  df <- as(sample_data(phy), "data.frame")
  pairs <- data.frame(t(combn(levels(df$Species), 2)), stringsAsFactors=F)
  p.pairs <- setNames(rep(NA, nrow(pairs)), with(pairs, paste(X1, X2, sep='-')))
  for (i in 1:nrow(pairs)) {
    dfs <- subset(df, Species %in% c(pairs[i,1], pairs[i,2]))
    dmats <- dmat[rownames(dfs), rownames(dfs)]
    set.seed(152470)
    permanova <- adonis(dmats ~ Species, data=dfs, permutations=999)
    p.pairs[i] <- permanova$aov.tab$`Pr(>F)`[1]
  }
  # Return letters signifying differences 
  return(multcompLetters(p.pairs))
}

sppdiffs97 <- sppdiffs(phy97.f.t)
sppdiffs100 <- sppdiffs(phy100.f.t)

sppdiffs <- data.frame("97% OTUs"=sppdiffs97$Letters, "100% OTUs"=sppdiffs100$Letters, check.names=F)
knitr::kable(sppdiffs, caption="Species not sharing a letter are significantly different (p < 0.05)")
```

## Differences between shores
Whether *Symbiodinium* communities differ between north vs. south shores within species is tested here using PERMANOVA.

```{r shorediffs, cache=T}
# Compute within- and between-shore statistics for each Species
shorestats <- data.frame(matrix(dimnames=list(levels(data.frame(sample_data(phy97.f.t))$Species), 
                                              c("Species", "n", "overall", "within", 
                                                "between", "R2", "bd", "p")), ncol=8, nrow=10))
for (i in 1:nlevels(data.frame(sample_data(phy97.f.t))$Species)) {
  sp <- levels(data.frame(sample_data(phy97.f.t))$Species)[i]
  shorestats$Species[i] <- sp
  phy97.f.t.species <- subset_samples(phy97.f.t, Species==sp)  # Set temp phyloseq object
  shorestats$n[i] <- nsamples(phy97.f.t.species)
  md <- meandist(phyloseq::distance(phy97.f.t.species, "bray"), 
                 sample_data(phy97.f.t.species)$Shore)
  shorestats$within[i] <- summary(md)$W  # Weighted mean dissimilarity within both Pools
  shorestats$between[i] <- summary(md)$B  # Mean dissimilarity between Pools
  shorestats$overall[i] <- summary(md)$D  # Overall dissimilarity
  if (nlevels(as(sample_data(phy97.f.t.species), "data.frame")$Shore) > 1) {
    set.seed(70235)
    permanova <- adonis(phyloseq::distance(phy97.f.t.species, "bray") ~ Shore, 
                        data=as(sample_data(phy97.f.t.species), "data.frame"), permutations=999)
    shorestats$R2[i] <- permanova$aov.tab$"R2"[1]  # PERMANOVA partial R-squared
    shorestats$p[i] <- permanova$aov.tab$"Pr(>F)"[1]  # PERMANOVA p-value
    bd <- betadisper(phyloseq::distance(phy97.f.t.species, "bray"),
                     group=as(sample_data(phy97.f.t.species), "data.frame")$Shore)
    shorestats$bd[i] <- TukeyHSD(bd)$group[4]
  } else {
    shorestats$R2[i] <- NA
    shorestats$p[i] <- NA
    shorestats$bd[i] <- NA
  }
}
knitr::kable(shorestats)  # dendrogyra, porites furcata, and siderastrea siderea differ by shore
```

## Beta diversity
Beta diversity is evaluated here as the multivariate dispersion of samples within a coral species group. Principal coordinate analysis on Bray-Curtis dissimilarities is used to calculate average distance-to-centroid values for each species group, which are then compared statistically by a permutation test. This analysis is implemented using betadisper() in the vegan package, based on [Anderson (2006)](dx.doi.org/10.1111/j.1541-0420.2005.00440.x).
```{r betadisper, cache=T, fig.width=4, fig.height=4}
# Calculate distances to species centroids for each sample in principal coordinate space
sambd <- betadisper(d=vegdist(t(otu_table(phy97.f.t)), method="bray"), 
                    group=data.frame(sample_data(phy97.f.t))$Species, type="centroid",
                    bias.adjust=TRUE)
# Calculate each species' mean distance to centroid and standard error
sambdsumm <- aggregate(data.frame(mean=sambd$distances), by=list(group=sambd$group), FUN=mean)
sambdsumm$se <- aggregate(sambd$distances, by=list(group=sambd$group), 
                      FUN=function(x) sd(x)/sqrt(length(x)))$x
# Determine order of decreasing mean dispersion
sambdsumm.ord <- sambdsumm[order(sambdsumm$mean, decreasing=T), ]
# Update betadisper object with species in decreasing order of mean dispersion
sambd <- betadisper(d=vegdist(t(otu_table(phy97.f.t)), method="bray"), 
                    group=factor(data.frame(sample_data(phy97.f.t))$Species, levels=as.character(sambdsumm.ord$group)), type="centroid", bias.adjust=TRUE)
# Use permutations to perform pairwise comparisons of group mean dispersions
sampt <- permutest(sambd, pairwise=T)
saml <- multcompLetters(sampt$pairwise$permuted)

@@

```{r strigosa}
dstr97 <- subset_samples(phy97.f.p, Species=="strigosa")
plot_bar(dstr97, x="Sample", y="Abundance", fill="OTU")
plot_bar(dstr97, x="Sample", y="Abundance", fill="Subtype")
# D strigosa hosted B1, B24, B35, B38, and C3 in Finney et al.... B25, B35, and B38 are missing from ref database.
# Also try 100% OTUs -- must filter more first...
dstr100.f <- subset_samples(phy100.f, Species=="strigosa")
dstr100.f.p <- transform_sample_counts(dstr100.f, function(x) x/sum(x))
#dstr100.f.p.f <- prune_taxa(rownames(otu_table(dstr100.f.p))[which(rowSums(otu_table(dstr100.f.p)) > 0.01)],
#                            dstr100.f.p)
#  
#plot_bar(dstr100.f.p.f, x="Sample", y="Abundance", fill="OTU")
#plot_bar(dstr100, x="Sample", y="Abundance", fill="Subtype")
#sample_names(dstr100.f)
#subset_samples(dstr100, Sample=="7")
#otu_table(dstr100.f)
#dstr100.f.p <- transform_sample_counts(dstr100.f, function(x) x/sum(x))
#colSums(otu_table(dstr100.f.p)[rowSums(otu_table(dstr100.f.p)) > 0.1, ])

@@

```{r otu_barplots_custom}
# 100%-OTUs barplot 
par(mar=c(2,3,4,1))
samdat <- data.frame(sample_data(dstr100.f.p))
typerelabund <- as.matrix(otu_table(dstr100.f.p)[order(data.frame(tax_table(dstr100.f.p))$Subtype), 
                                                 rownames(samdat)])

# Get info for plotting OTU names and blast hits on top of barplot
blasthits <- as.character(data.frame(tax_table(dstr100.f.p))[order(data.frame(tax_table(dstr100.f.p))$Subtype)
                                                             , "Subtype"])
names <- as.character(rownames(data.frame(tax_table(dstr100.f.p)))[order(data.frame(tax_table(dstr100.f.p))$Subtype)])
divides <- apply(typerelabund, 2, cumsum)
heights <- diff(divides)
heights[heights < 0.04] <- NA

# Plot barplot and OTU names and blast hits
bars <- barplot(typerelabund, col=rainbow(941), border=NA, las=1, xlab="Sample", ylab="", cex.axis=0.75, cex.names=0.75)
mtext(side=2, text = "Relative Abundance", line=2)
for (i in 1:length(bars)) {
  text(rep(bars[i], length(heights[which(!is.na(heights[,i])),i])), 
       divides[which(!is.na(heights[,i])),i] + heights[which(!is.na(heights[,i])),i] / 2, 
       labels=paste(names[which(!is.na(heights[,i]))+1],blasthits[which(!is.na(heights[,i]))+1],sep="\n"),
       cex=0.6)
}

mtext(side=3, "B.) 100% OTUs", xpd=T, adj=0, line=2.5, font=2)

@@
